---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  warning = FALSE,
  message = FALSE,
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/",
  out.width = "100%"
)
```

# R code from: J端rgens and Eckert (2024)
![](https://img.shields.io/badge/manuscript-submitted-blue.svg)
![](https://img.shields.io/badge/repo%20status-private-orange.svg)

# :open_file_folder: Repository Structure
* **Working_data/:** Contains the initial R script to download and unzip the data archived at [zenodo](https://zenodo.org/)
* **Analysis_BMA/:** Contains all R scripts to analyse the broth microdilution assay (BMA) dataset
* **Analysis_LCMS/:** Contains all R scripts to analyse the liquid chromatography-mass spectrometry (LCMS) dataset

# :package: Dependencies
To be able to smoothly reproduce the figures and tables, make sure you have [R v4.3.3](https://cran.uni-muenster.de/index.html) and the necessary packages installed:
```{r packages, eval = FALSE}
install.packages(c("here", "microdiluteR", "dplyr", "tidyr", "ggplot2", "ggpubr", "cowplot", "vegan", "reshape2"))
```

# :arrow_forward: Quick start

To reproduce the analyses and visualizations from the manuscript in a structured and guided manner:

1. **Download** [R v4.3.3](https://cran.uni-muenster.de/index.html) and [RStudio](https://posit.co/download/rstudio-desktop/).
2. **Clone the repository** via [Git](https://docs.github.com/en/repositories/creating-and-managing-repositories/cloning-a-repository), [VS code](https://learn.microsoft.com/en-gb/azure/developer/javascript/how-to/with-visual-studio-code/clone-github-repository?tabs=activity-bar) or [RStudio](https://argoshare.is.ed.ac.uk/healthyr_book/clone-an-existing-github-project-to-new-rstudio-project.html).
3. **Keep the structure** as it is, don't rename the folders or R scripts that are already present.
4. **Open the `.Rproj` file** in RStudio to initiate the cloned repository as an RStudio project. This will enable all R scripts to automatically detect the root directory of the project.
5. **Run the `R_download_zenodo_archive.R` script** with `CTRL+ALT+R` to download the stored data from the corresponding [zenodo](https://zenodo.org/) repository. You don't have to change the settings, since the data will be automatically downloaded and unzipped into the `Working_data` folder.
6. **Analyze BMA data** by running the `R_Figure_1.R` and `R_Table_S2.R` scripts. Two new folders `Figures` and `Tables` will emerge storing the corresponding figures and tables from the manuscript.
7. **Analyze LCMS data** by running the scripts `R_tidy_LCMS_data.R`, `"R_Figure_2.R` and `R_Tables_1_and_S3.R` sequentially. Additional figures and tables will be added to the folders `Figures` and `Tables`.

# :pushpin: Citation
**Citing this repository:**

>J端rgens, J., & Eckert, S. (2024). R code from: Foliar 5-azacytidine treatment of Tanacetum vulgare chemotypes alters in vitro growth performance of the necrotrophic fungus Botrytis cinerea [Computer software]. https://github.com/silvia-eckert/J-rgens_Eckert_2024_FREAE

**Citing the corresponding manuscript:**

>J端rgens, J., & Eckert, S. (2024). Foliar 5-azacytidine treatment of _Tanacetum vulgare_ chemotypes alters in vitro growth performance of the necrotrophic fungus _Botrytis cinerea_. Frontiers in Epigenetics and Epigenomics (Submitted).

**Citing the dataset deposited on Zenodo:**

>J端rgens, J., & Eckert, S. (2024). Data from: Foliar 5-azacytidine treatment of _Tanacetum vulgare_ chemotypes alters in vitro growth performance of the necrotrophic fungus _Botrytis cinerea_. _Zenodo_. DOI:

# :scroll: License
This repository and the files therein are licensed under the [GPL-3.0 license](https://www.gnu.org/licenses/gpl-3.0.html.en).

